A holomorphic approach to branes in twisted~$M$-theory

### 2022-09-20 fivebranes/intro.tex
abstract

\documentclass[11pt]{amsart}

\linespread{1.15} %for editing

%\usepackage{../macros-master}
\usepackage{macros-fivebrane}

\begin{document}

@@

Proceeding as in the abelian case, we can place the factorization algebra $\Obs_{A_1}$ on $\C^\times \times \C^2$ and compactifying $S^1 \subset \C^\times$ to obtain an associative dg algebra $\oint_{S^1} \Obs_{A_1}$.
From our conjectural description of $\Obs_{A_1}$ (we denote this factorization algebra by $\til\Obs_2$ in the body of the paper) given in \S \ref{s:fact}, one can see that this classical limit of the associative dg algebra is of the form
\beqn
U \left(\cE(3|6)|_{\C^\times \times \C^2}\right) .
\eeqn
This is meant to indicate the enveloping algebra of a super Lie algebra $\cE(3|6)|_{\C^\times \times \C^2}$ which is a `punctured' version of the exceptional simple super Lie algebra $E(3|6)$. 
In particular, $E(3|6)$ sits inside this super Lie algebra as the positive modes.
Again, in this paper we will only discuss a certain classical limit of the true factorization algebra associated to the holomorphic twist of the six-dimensional theory. 
At the quantum level, we expect that the algebra gets deformed to the enveloping algebra of a certain ($L_\infty$) central extension of this super Lie algebra.

>>>>

%\documentclass[11pt]{amsart}
%
%\linespread{1.15} %for editing
%
%%\usepackage{../macros-master}
%\usepackage{macros-fivebrane}

%\begin{document}

@@

Proceeding as in the abelian case, we can place the factorization algebra $\Obs_{A_1}$ on $\C^\times \times \C^2$ and compactify $S^1 \subset \C^\times$ to obtain an associative dg algebra $\oint_{S^1} \Obs_{A_1}$.
From our conjectural description of $\Obs_{A_1}$ (we denote this factorization algebra by $\til\Obs_2$ in the body of the paper) given in \S \ref{s:fact}, one can see that this classical limit of the associative dg algebra is of the form
\beqn
U \left(\cE(3|6)|_{\C^\times \times \C^2}\right) .
\eeqn
This is meant to indicate the enveloping algebra of a super Lie algebra $\cE(3|6)|_{\C^\times \times \C^2}$ which is a `punctured' version of the exceptional simple super Lie algebra $E(3|6)$. 
In particular, $E(3|6)$ sits inside this super Lie algebra as the positive modes.
Again, in this paper we will only discuss a certain classical limit of the true factorization algebra associated to the holomorphic twist of the six-dimensional theory. 
At the quantum level, we expect that the algebra gets deformed to the enveloping algebra of a certain ($L_\infty$) central extension of this super Lie algebra.

### 2022-09-20 fivebranes/main.tex
outline
all around
removed preambles in included files, formatting
merge
main
abstract

%\linespread{1.2} %for editing

@@

\title{}

\input{index}

>>>>

\linespread{1.15} %for editing

@@

\title{A holomorphic approach to branes in twisted~$M$-theory}
\maketitle

\begin{abstract}
We present a conjectural description of the algebra of operators on a stack of finitely many fivebranes in $M$-theory at the level of the holomorphic twist.
Our approach is through the lens of twisted holography and utilizes a description of the minimal twist of eleven-dimensional supergravity. 
From the conjectural description of local operators we deduce closed formulas for the superconformal index of six-dimensional theories of type $A_{N-1}$.
\end{abstract}

\setcounter{tocdepth}{1}
\tableofcontents

\input{intro}

\subsection*{Acknowledgements}
We thank K.~Costello, D.~Gaiotto, F.~Hahner, Si Li, N.~Paquette, and P.~Yoo for conversations and discussions about ideas that helped lead to the completion of this work. 
Special thanks are due to Ingmar Saberi for his collaborations on past, current, and future related projects.
The work of S.R. ...
The work of B.W. was supported by Boston University and the University of Edinburgh. 
%Twisted supergravity
\input{twisted}

%The character of holomorphic local operators
%%introduce local operators for hol/top theories.
%%introduce hol characters for hol/top theories. 
%%example of a single fivebrane
%%example of a single membrane
%%Large N limit.
\input{index}

%Factorization algebras in twisted M theory
%%`Restricted' factorization algebra.
%%Koszul duality.

\input{fact}
%A holographic decomposition of local operators
%%E(3|6) decomposition of local operators. 
%%character computations following KR resolutions.
%%E(1|6) decomposition of local operators. 
%%some finite N membrane indices??

\input{ops}

\input{finite}

%%backreaction for single fivebrane.

%%\input{??}

\printbibliography
